---
title: "Basic Example Report - HPAI"
date-modified: today
author: "GVPHU Epidemiology, Data and Analytics team"
format: 
  html:
    code-fold: true
    code-overflow: scroll
    code-tools: true
execute: 
  echo: false
  message: false
  warning: false
---


```{r}
#| label: setup
#| echo: false
#| message: false
#| warning: false

pacman::p_load(tidyverse,
               janitor,
               here,
               readxl,
               rio,
               showtext,
               gt,
               ggrepel,
               gtsummary,
               sf,
               leaflet,
               leaflet.extras)


# Setting GV theme
gv_colours <- list(
  "dark_blue" = "#00416B",
  "med_blue" = "#0E4C90",
  "light_blue" = "#0075C9",
  "purple" = "#9D57A3",
  "black" = "#424143",
  "grey" = "#EAEAEA",
  "white" = "#FFFFFF",
  "aqua" = "#00b0ab",
  "aqua2" = "#89CCC8",
  "dark_aqua" = "#008aab",
  "dark_aqua2" = "#78B8C9",
  "bright_orange" = "#e75300",
  "dark_red"="#ac162c",
  "dark_pink" = "#b52372",
  "green" = "#84BD00",
  "green2" = "#BED99A",
  "orange" = "#FFA300",
  "orange2" = "#FFC594",
  "dark_purple" = "#470A68",
  "light_purple" = "#A192B2",
  "red" = "#b01c2e",
  "red2" = "#CA9699",
  "cool_grey" = "#646569",
  "cool_grey2" = "#A8A8A9"
)


# basic theme elements ----------------------------------------------------

theme_gv <- function() {
  
  theme_minimal() +
    theme(text = element_text(family = "cabin"),
          axis.title = element_blank(),
          axis.text.x = element_text(face = "bold",
                                     margin = margin(t = -5)),
          legend.title = element_blank())
}



font_add_google("Cabin", "cabin")

showtext_auto()

theme_set(theme_gv())

source(here::here("code", "04_Cleaning for reporting and PHESS.R"))

```

```{r}
#| label: text_calc
#| echo: false
#| message: false
#| warning: false

# Number of IP sites
n_ip_sites <- 1

# Total (unique) contacts screened
n_total_contacts_pre_triage <- nrow(redcap)

# Total contacts triaged (completed)
n_total_contacts_responded_triage <- dat_clean %>%
  filter(!is.na(exposure_ip1_yn) | !is.na(exposure_ip2_yn)) %>%
  nrow()

# Total contacts triaged (attended)
n_total_contacts_exposed <- dat_clean %>%
  filter(exposure_ip1_yn == 1 | exposure_ip2_yn == 1) %>%
  nrow()

pc_total_contacts_exposed <- (n_total_contacts_exposed/n_total_contacts_responded_triage * 100)

# Total contacts interviewed (3 PHO led interview forms marked as 'complete')
n_contacts_interviewed <- dat_clean %>%
  filter(avian_influenza_case_demo_complete == 2 & 
           (avian_influenza_case_facility_ip1_risk_complete == 2 | avian_influenza_case_facility_ip2_risk_complete == 2) &
  avian_influenza_case_symptoms_treatment_complete == 2) %>%
  nrow()

pc_contacts_interviewed <- (n_contacts_interviewed/n_total_contacts_exposed * 100)


# Total high risk contacts
n_high_risk <- dat_clean %>%
  filter(exposure_risk_calculated_all == "High Risk") %>%
  nrow()

# Total with any symptoms
n_symptoms_any <- dat_clean %>%
  filter(symptoms == 1 | symptoms_yn_fu == 1) %>%
  nrow()

# Total in high risk period
# Filter to last high risk exposure in the last 10 days
date_10_days_ago <- Sys.Date() - 10 # Calculate the date 10 days ago from today


n_high_risk_period <- dat_clean %>%
  filter(exposure_risk_calculated_all == "High Risk") %>%
  filter(last_exposure_date_all >= date_10_days_ago) %>%
  nrow()  
```

## Local Public health Unit

* `r n_ip_sites` HPAI infected premises have been reported  
* After deduplication, a total of `r n_total_contacts_pre_triage` contacts were provided by facilities for screening; to date `r n_total_contacts_responded_triage` have been triaged, with `r n_total_contacts_exposed` (`r round(pc_total_contacts_exposed, 2)`%) having reported attendance onsite during the period of interest  
* `r n_contacts_interviewed` (`r round(pc_contacts_interviewed, 2)`%) of those who have reported onsite attendance during the period of interest had their interview completed  
* `r n_high_risk` have been identified as high risk and `r n_symptoms_any` have reported symptoms  
* `r n_high_risk_period` high risk contacts are still in their high risk period requiring follow up

```{r}
#| label: summary_table
#| echo: false
#| message: false
#| warning: false

dat_ip <- dat_clean %>%
  pivot_longer(
    cols = c(exposure_ip1_yn, exposure_ip2_yn),
    names_to = "ip_site",
    values_to = "exposed"
  ) %>%
  filter(exposed == 1) %>%
  mutate(
    ip_site = recode(ip_site,
                     exposure_ip1_yn = "IP1",
                     exposure_ip2_yn = "IP2")
  )

summary_ip <- dat_ip %>%
  group_by(ip_site) %>%
  summarise(

    # Total contacts
    `Total Contacts` = n(),

    # Suspected cases
    `Suspected Cases` = sum(symptoms == 1 | symptoms_yn_fu == 1, na.rm = TRUE),

    # Confirmed cases
    `Total Cases (confirmed)` = sum(
      (symptoms == 1 | symptoms_yn_fu == 1) &
      test_results %in% c(2, 3),
      na.rm = TRUE
    ),

    # High risk contacts
    `High Risk Contacts` = sum(
      exposure_risk_calculated_all == "High Risk",
      na.rm = TRUE
    ),

    # Final contact at risk date
    `Final contact at risk date` = max(last_exposure_date_all, na.rm = TRUE)

  ) %>%
  ungroup()

summary_ip
```
